elton trait

### 2019-07-05 data-raw/elton.Rmd
Rename was adding an extra matchingName column.

comm_matches <- bird_ids  %>%
  filter(match_type == "common") %>%
  select(id = acceptedNameUsageID, input, scientificName) %>%
  distinct() %>%
  right_join(bird_trait %>% filter(!specid %in% sci_matches$specid) %>% select(.dots = -col_ex), by = c("input" = "english"), na_matches = "never") %>%
  distinct() %>%
  rename(matchingName = input) %>%
  select(-scientific)

>>>>

comm_matches <- bird_ids  %>%
  filter(match_type == "common") %>%
  select(id = acceptedNameUsageID, input, scientificName) %>%
  distinct() %>%
  right_join(bird_trait %>% filter(!specid %in% sci_matches$specid) %>% select(.dots = -col_ex), by = c("input" = "english"), na_matches = "never") %>%
  distinct() %>%
  select(-scientific)
